### 2020-03-25 paper/conclusion.tex
before submission

\section{Conclusion} \label{Conclusion}
In the current work, we proposed a reactivity control system design for the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for the full-core geometry using the
SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions of 
the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU, extracted from \gls{LWR} \gls{SNF}.

@@

Six different absorbing materials are considered in this work:
natural B$_4$C, B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
with TRU vector from \gls{LWR}. The reason for this is the much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

@@

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case), this makes the SSD clusters unreliable to shut down the reactor loaded 
with TRU because the SSD clusters should provide a sufficient positive shutdown margin.

>>>>

\section{Conclusion} \label{Conclusion}
In the current work, we proposed a reactivity control system design for the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for the full-core geometry using the
SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions:
(1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU, extracted from \gls{LWR} \gls{SNF}.

@@

Six different absorbing materials are considered in this work:
natural B$_4$C, B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both Control Safety Devices (CSD)
and Shutdown Safety Devices (SSD) clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
with TRU from \gls{LWR}. The reason for this is the much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

@@

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case).

### 2020-03-25 paper/results.tex
before submission

Table~\ref{tab:excess}

@@

We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (CR clusters located in the center and at the boundary between the core
zones, see Figure~\ref{fig:core_25}) to investigate the variation of CRW with the position in the inner core.
The CRW decreases in the direction of the outer core zone. The outer core zone 
has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
($2.8$); consequently, the neutron energy spectrum is faster in the peripheral 
zone than in the center of the core degrading the CR's 
absorption ability in that region.

@@

The SSD clusters are designed mainly for an emergency shutdown, thus it should 
provide the reactor core with sufficient negative reactivity. The 
shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.
Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core 
initially loaded with $^{233}$U, reactor-grade Pu, and TRU 
elements for different absorbing materials. All absorbing materials provide a sufficient positive
SDM for the SD-TMSR core that is initially loaded with 
$^{233}$U and reactor-grade Pu. However, the SDMs for the TRU case are 
negative or slightly positive (in B$_4$C-90 case); this makes the SSD clusters 
unreliable to shut down the reactor loaded with TRU.
As mentioned previously, the SSD clusters should 
provide a sufficient positive SDM.

\begin{table}  [!hb]
	\caption{The SDMs for the SD-TMSR core for different absorbing materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{3cm} s s s}
		\hline
		Absorbing materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		Nat. B$_4$C					& $12.62\pm0.08$ $\$$ &$10.18\pm0.09$ $\$$ &$-1.12\pm0.08$ $\$$ \\
		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ & $ $ $ $ $1.01\pm0.09$ $\$$ \\
		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.80\pm0.09$ $\$$\\
		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.890\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. The strongest anti-shadowing effect occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratios (see Table~\ref{tab:worth}).
The obtained results emphasize that no relation exists between the absorbing
material type and the interference between the CR clusters
(i.e., the A$_{CRi}$).

@@

Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with six 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper half of the core 
($<250$ cm from the upper boundary of the core). Further insertion of the 
CRs demonstrates that the strongest absorber, B$_4$C-90 outperforms other materials.
Notably, all results are based on steady state calculations.

>>>>

@@

We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (i.e. clusters located in the center and at the boundary between the core
zones, see Figure~\ref{fig:core_25}) to investigate the variation of CRW with the position in the inner core.
The CRW decreases in the direction of the outer core zone. The outer core zone 
has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
($2.8$); consequently, the neutron energy spectrum is faster in the peripheral 
zone than in the center of the core degrading the CR's 
absorption ability in that region.

@@

The Shutdown Safety Devices (SSD) clusters are designed mainly for an emergency shutdown, thus it should 
provide the reactor core with sufficient negative reactivity. The 
shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.
Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core 
initially loaded with $^{233}$U, reactor-grade Pu, and TRU 
elements for different absorbing materials. All absorbing materials provide a sufficient positive
SDM for the SD-TMSR core that is initially loaded with 
$^{233}$U and reactor-grade Pu. However, the SDMs for the TRU case are 
negative or slightly positive (in B$_4$C-90 case); this makes the SSD clusters 
unreliable to shut down the reactor loaded with TRU.
As mentioned previously, the SSD clusters should 
provide a sufficient positive SDM.

\begin{table}  %[!hb]
	\caption{The SDMs for the SD-TMSR core for different absorbing materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{3cm} s s s}
		\hline
		Absorbing materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		Nat. B$_4$C					& $12.62\pm0.08$ $\$$ &$10.18\pm0.09$ $\$$ &$-1.12\pm0.08$ $\$$ \\
		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ & $ $ $ $ $1.01\pm0.09$ $\$$ \\
		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.80\pm0.09$ $\$$\\
		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.890\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. The strongest anti-shadowing effect occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratios (see Table~\ref{tab:worth}).
The obtained results emphasize that no relation exists between the absorbing
material type and the interference between the CR clusters
(i.e. the A$_{CRi}$).

@@

Figure~\ref{fig:CSD} shows the integral CRW for only Control Safety Devices (CSD) clusters with six 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper half of the core 
($<250$ cm from the upper boundary of the core). Further insertion of the 
CRs demonstrates that the strongest absorber, B$_4$C-90 outperforms other materials.
Notably, all results are based on steady state calculations.
